Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-12 results.tex
added JG reasoning about col arima to results

Note that the \col points (blue {\color{blue}$+$} icons) are clustered
very tightly in the lower left quadrant of the LMA and \naive ~$MASE$
vs. WPE plots, but spread out horizontally in the ARIMA plot.  This is
because of the way that these models are built.  If a KPSS test of the
time series in question indicates that it is nonstationary, an
integration term is added to the model.  According to this test, the
\col time series is right on the edge of nonstationarity, so the ARIMA
procedure sometimes omits the integration term, which increases the
error, thereby spreading out the points.

>>>>

Note that the \col points (blue {\color{blue}$+$} icons) are clustered
very tightly in the lower left quadrant of the LMA and \naive ~$MASE$
vs. WPE plots, but spread out horizontally in the ARIMA plot.  This is
because of the way that these models are built \cite{auto-arima}.  If
a KPSS test of the time series in question indicates that it is
nonstationary, an integration term is added to the model.  This test
gives mixed results in the case of the \col process, flagging five of
the 15 trials as stationary and ten as nonstationary.  ARIMA models
without an integration term perform more poorly on this signal, which
increases the error, thereby spreading out the points\footnote{We
  tested this hypothesis by forcing the inclusion of an integration
  term in the five cases where a KPSS test indicated that such a term
  was not needed.  This action removed the spread, pushing all 15 of
  the \col ARIMA points in Figure~\ref{fig:wpe_vs_mase_all} into a
  tight cluster.}.
